background points - is more better?

### 2019-01-08 src/background_points_no_check.Rmd
updated for new background dataset (inc new output folder which is more organised)

netcdf_list <- list.files("../data/bktstncdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/bktstncdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
yr <- 2007  # a variable for the observation year
mth <- 10  # a variable for the observation month

for (i in 1:no_netcdf) {  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  brkvar <- (sapply(strsplit(netcdf_name[i], "_"), "[[", 3)) # extracting the third part of the netcdf (inc.nc)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(testbk190000sp)) {  
      de <- testbk190000sp$depthlayerno[[j]]  # a variable for the observation depth layer
          if (brkyr == yr & brkmth == mth & brkvar == "temp.nc"){
              testbk190000sp$temp_surface[j] <- extract(x=temp_brick[[1]], y = testbk190000sp[j, ]) 
              if (is.na(de)){
                testbk190000sp$temp_depth[j] <- NA
              } else  
                testbk190000sp$temp_depth[j] <- extract(x=temp_brick[[de]], y = testbk190000sp[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "salinity.nc") {
              testbk190000sp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = testbk190000sp[j, ]) 
              if (is.na(de)){
                testbk190000sp$salinity_depth[j] <- NA
              } else  
                testbk190000sp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = testbk190000sp[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "chl.nc") {
              testbk190000sp$chl_surface[j] <- extract(x=temp_brick[[1]], y = testbk190000sp[j, ]) 
              if (is.na(de)){
                testbk190000sp$chl_depth[j] <- NA
              } else  
                testbk190000sp$chl_depth[j] <- extract(x=temp_brick[[de]], y = testbk190000sp[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "o2.nc") {
              testbk190000sp$o2_surface[j] <- extract(x=temp_brick[[1]], y = testbk190000sp[j, ]) 
              if (is.na(de)){
                testbk190000sp$o2_depth[j] <- NA
              } else  
                testbk190000sp$o2_depth[j] <- extract(x=temp_brick[[de]], y = testbk190000sp[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "mlp.nc") {
              testbk190000sp$mlp_surface[j] <- extract(x=temp_brick[[1]], y = testbk190000sp[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "ssh.nc") {
              testbk190000sp$ssh_surface[j] <- extract(x=temp_brick[[1]], y = testbk190000sp[j, ])

@@

netcdf_list <- list.files("../data/bktstncdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/bktstncdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
yr <- 1999  # a variable for the observation year
mth <- 02  # a variable for the observation month

@@

netcdf_list <- list.files("../data/bktstncdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/bktstncdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
yr <- 2014  # a variable for the observation year
mth <- 06  # a variable for the observation month

>>>>

netcdf_list <- list.files("../data/env/bktstncdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/bktstncdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
yr <- 2007  # a variable for the observation year
mth <- 10  # a variable for the observation month

@@

netcdf_list <- list.files("../data/env/bktstncdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/bktstncdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
yr <- 1999  # a variable for the observation year
mth <- 02  # a variable for the observation month

@@

netcdf_list <- list.files("../data/env/bktstncdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/bktstncdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
yr <- 2014  # a variable for the observation year
mth <- 06  # a variable for the observation month
